Statistics Project

### 2022-12-10 rough_analysis.Rmd
Updated prediction models, added Kaggle scores from submitted material

The rudimentary approach of numeric/reduced linearity set receives a Kaggle score of 0.20855. While is is interesting and good given the novel approach of the selection model, it's troubling to see that all 3 models returned the exact same Kaggle score, down to the last decimal. This may indicate that the models are adding/subtracting parameters to result in the exact same parameter list each time. This should be further investigated.

>>>>

The rudimentary approach of numeric/reduced linearity set receives a Kaggle score of 0.20
